A framework for mentored data science research

### 2019-12-09 Rmd/results.Rmd
expanded discussion
fixed results

# Outcomes

We applied the project framework to our mentoring of two students. 
Both engaged in 12 months of mentored research during their senior year of 
undergraduate studies in statistics.

@@

Both students secured positions in data science after graduation. 
One student later enrolled in a statistics graduate program, 
while the other pursued employment in health care analytics.

@@

Our scholarly contributions include the `parseTweetFiles` R package on Github
(https://github.com/rturn/parseTweetFiles) and presentations at conferences such as useR! 2016 and local poster sessions. Additionally, both students prepared end-of-project reports on their research.

We consider below

>>>>

# Results

We applied the project framework to our mentoring of two students. 
Both engaged in 12 months of research during their senior year of 
undergraduate studies in statistics. Below, we describe three categories of outcomes:

1. student outcomes
1. mentor outcomes
1. scholarly outcomes

@@

Both students secured positions in data science after graduation. 
One student enrolled in a statistics graduate program, 
while the other pursued employment in health care analytics.

## Mentor outcomes

We (Boehm and Hanlon) grew as mentors during our work with the two students. We successfully
guided junior scientists through a productive, hands-on research experience, and we anticipate
refining the framework in future iterations.

@@

Our scholarly contributions include the `parseTweetFiles` R package on Github
(https://github.com/rturn/parseTweetFiles) and presentations at conferences such as useR! 2016 (R users' conference)
and local poster sessions. Additionally, both students prepared end-of-project reports on 
their research.
